### 2018-03-17 paper/7-related.tex
Minor changes
Add some text on self-adjusting computation

\todo{AM}{Write a short section about memoization if enough time.}
% \subsection{Memoization}\label{sec-related-memo}

@@

While not typically considered build systems, self-adjusting computation is a
well studied area, and in particular the contrast between different formulations
has been well studied.

\todo{AM}{Write this section.}

@@

\begin{minted}{haskell}
type Optic p a b s t = p a b -> p s t
\end{minted}

>>>>

% \todo{AM}{Write a short section about memoization if enough time.}
% \subsection{Memoization}\label{sec-related-memo}

@@

While not typically considered build systems, self-adjusting computation is a
well studied area, and in particular the contrast between different formulations
has been well studied~\cite{acar2007selfadjusting}.

Self-adjusting computations can automatically adjust to an external change
to their inputs. A classic example is a self-adjusting sorting algorithm, which
can efficiently (in $O(\log{n})$ time where $n$ is the length of the input)
recalculate the result given an incremental change of the input. While very
close to build systems in spirit, self-adjusting computations are mostly used
for in-memory computation and rely on the ability to dynamically allocate new
keys in the store for sharing intermediate computations~--~an intriguing feature
rarely seen in build systems (\Shake's oracles~\S\ref{sec-polymorphism} can be
used to model this to a limited degree).

A lot of research has been dedicated to finding efficient data structures and
algorithms for self-adjusting computations~--~we plan to explore this
untapped (by build systems) resource in~future.

@@

\begin{minted}[xleftmargin=10pt]{haskell}
type Optic p a b s t = p a b -> p s t
\end{minted}
